---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

What this is about:
I want to plot correlations between variables that were captured in a survey I did in December. I am interested in better ways to communicate correlations than the usual correlation tables I see in our journals.

```{r}

library(reshape2)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(Hmisc)
library(ggsn)
library(qgraph)
library(synthpop)
library(xlsx)
here::here()

data <- read_csv("data_syn.csv")

```

Using geom_tile

```{r}

cormat <- round(cor(data), 2)

melted_cormat <- melt(cormat)

ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "#b35806", high = "#542788", mid = "#f7f7f7", 
                      midpoint = 0, limit = c(-1, 1), space = "Lab", 
                      name="Correlation\nstrength") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1, size = 11, hjust = 1)) + 
  coord_fixed() +
  labs(x = "",
       y = "",
       title = "Pearson correlations")

```

This is OK, I don't like that it displays irrelevant and redundant information. It shows all correlations, including those that are insignificant, and the full table, i.e. upper and lower triangle. 

Using ggcorrplot package 

```{r}


cormat_pearson <- rcorr(as.matrix(data), type = "pearson")
p.mat <- cormat_pearson$P

ggcorrplot(cormat, method = "square", 
           type = "lower", 
           lab = TRUE,
           lab_size = 2,
           title = "Pearson correlations\nOnly significant (alpha < .05) correlations shown",
           hc.order = TRUE,
           outline.col = "white",
           p.mat = p.mat,
           sig.level = 0.05,
           insig = "blank") + 
  scale_fill_gradient2(low = "#542788", high = "#b35806", mid = "#f7f7f7", 
                      midpoint = 0, limit = c(-1, 1), space = "Lab", 
                      name = "Correlation\nstrength")

```

I am not sure about displaying the actual correlation strength, I might take that out.


Trying a network-like display:

```{r}

 gqgraph <- qgraph(cormat, 
        graph = "pcor", 
        layout = "circle", 
        minimum = "sig", 
        sampleSize = 99, 
        theme = "colorblind",
        edge.labels = TRUE)

#If I want to have this printable in black and white, I can make the negative lines dashed

makeBW(gqgraph, plot = TRUE)

```

Plus: 
Really easy way to see in one glance those correlations that stick out. However, I first did this with my real data and there were much fewer significant correlations. The plot was much more accessible when only half as many lines were displayed. 

Problems: 
Displayed numbers are sometimes behind labels and not legible (but I can just omit them but then you wouldn't know anymore what direction color signifies)
Variable names get shortened and I don't recognize them myself, having to guess what's what
It's hard to recognize if the lines connect variables that are next to each other versus separated by one other variable 

