---
title: "Untitled"
output: html_document
editor_options: 
  chunk_output_type: console
---

What this is about:
I want to plot correlations between variables that were captured in a survey I did in December. I am interested in better ways to communicate correlations than the usual correlation tables I see in our journals.

```{r}

library(reshape2)
library(tidyverse)
library(ggplot2)
library(ggcorrplot)
library(Hmisc)
library(ggsn)
library(qgraph)
library(synthpop)
library(xlsx)
here::here()

data <- read_csv("data_syn.csv")

```

Using geom_tile

```{r}

cormat <- round(cor(data), 2)

melted_cormat <- melt(cormat)

ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white") +
  scale_fill_gradient2(low = "#b35806", high = "#542788", mid = "#f7f7f7", 
                      midpoint = 0, limit = c(-1, 1), space = "Lab", 
                      name="Correlation\nstrength") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1, size = 11, hjust = 1)) + 
  coord_fixed() +
  labs(x = "",
       y = "",
       title = "Pearson correlations")

```

This is OK, I don't like that it displays irrelevant and redundant information. It shows all correlations, including those that are insignificant, and the full table, i.e. upper and lower triangle. 

Using ggcorrplot package 

```{r}


cormat_pearson <- rcorr(as.matrix(data), type = "pearson")
p.mat <- cormat_pearson$P

ggcorrplot(cormat, method = "square", 
           type = "lower", 
           lab = TRUE,
           lab_size = 2,
           title = "Pearson correlations\nOnly significant (alpha < .05) correlations shown",
           hc.order = TRUE,
           outline.col = "white",
           p.mat = p.mat,
           sig.level = 0.05,
           insig = "blank") + 
  scale_fill_gradient2(low = "#542788", high = "#b35806", mid = "#f7f7f7", 
                      midpoint = 0, limit = c(-1, 1), space = "Lab", 
                      name = "Correlation\nstrength")

```

I am not sure about displaying the actual correlation strength, I might take that out.


Trying a network-like display:

```{r}

 gqgraph <- qgraph(cormat, 
        graph = "pcor", 
        layout = "circle", 
        minimum = "sig", 
        sampleSize = 99, 
        theme = "colorblind",
        edge.labels = TRUE)

#If I want to have this printable in black and white, I can make the negative lines dashed

makeBW(gqgraph, plot = TRUE)

```

Plus: 
Really easy way to see in one glance those correlations that stick out. However, I first did this with my real data and there were much fewer significant correlations. The plot was much more accessible when only half as many lines were displayed. 

Problems: 
Displayed numbers are sometimes behind labels and not legible (but I can just omit them but then you wouldn't know anymore what direction color signifies)
Variable names get shortened and I don't recognize them myself, having to guess what's what
It's hard to recognize if the lines connect variables that are next to each other versus separated by one other variable 


Mike's comments:
Sophie, thanks for sharing your final project draft with me.  I enjoyed reviewing your script and draft visualizations and am looking forward to your final presentation next week.  Following are some comments (organized by letter in the assignment instruction on the course website):

Strengths (a):
1.  Its exciting to see data from an actual student project visualized.  My project used data publicly available on the internet, which has utility, but I think its much more interesting to view visualizations tied to data that has personal meaning to you.
2.  I like that you are thinking outside the box in terms of visualizating the same old correlation matrices we see in our top journals, and your three visualizations give three exciting opportunities to do just that.  Assuming your project is intended for an academic audience, it would be exciting for them to latch onto one or more of these.  Each of these seems to hold good potential for use at a conference or even article submission.  Additionally, your three chosen visualizations are very good options for the data you are representing.
3.  I appreciate the comments you leave throughout the RMD file, both within the chunks of code and between them.  This is especially helpful for an outside reader like me to use in following your train of thought and decision process as you have iterated onto the three different visualizations.
  

Learning from script (b):
1.  I appreciate how you have divided your script up into meaningful chunks.  Each chunk serves a specific purpose, from package loadings to separate chunks for each visualization.  This presents a clean and orderly flow that makes your script very easy to follow.
2.  I also like the clean way you manage your script through indentations and lowercase type.  These stylistic choices also help an external reviewer in working through your script choices.
3.  Finally, I enjoyed the novelty of the network display of correlations.  This is unlike anything I have encountered before in this context, and I will definitely dig deeper into the qgraph package from your code for future use in my own projects.


Suggestions (c):
I know these are working drafts, so these suggestions are probably nothing you haven't already considered.
1.  Variables.  I wonder how you could more explicitly explain what the variables are for the uninformed reader.  Are there natural groupings?  Could you highlight the DV?  Could a final draft streamline these a little and only include or highlight those that are most salient, maybe with gghighlight?
2.  Colors.  The network diagram uses red and blue, which intuitively to me communicate good/bad.  Is this the intended message of the negative values?  If not, perhaps a different color scheme would help redirect my natural interpretations.
3.  Labels.  Also of benefit to the uninformed reader could be the use of titles, subtitles, or captions to explain and direct my attention further.

Great work, and good luck on your final project!

Mike